A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-10 bidir_pathtrace_skeleton.tex
Change title + add some notes in the intro

\title{A 3d curvilinear skeletonization algorithm with application to bidirectional path tracing}
\author{John Chaussard\inst{1} \and Laurent No\"{e}l\inst{2} \and Venceslas Biri\inst{2} \and Michel Couprie\inst{2}}
\institute{Universit\'{e} Paris 13, Sorbonne Paris Cit\'{e}, LAGA, CNRS(UMR 7539), \\ F-93430, Villetaneuse, France \\ \email{chaussard@math.univ-paris13.fr}
\and
Universit\'{e} Paris Est, LABINFO-IGM, A3SI-ESIEE \\ 2, boulevard Blaise Pascal, Cit\'{e} DESCARTES \\ BP 99  93162 Noisy le Grand CEDEX, France \\ \email{laurent.noel@esiee.fr, v.biri@esiee.fr, michel.couprie@esiee.fr}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                        %
%                   INTRODUCTION                         %
%                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec::intro}
Blah blah blah...

>>>>

\title{A 3d curvilinear skeletonization algorithm with application to path tracing}
\author{John Chaussard\inst{1} \and Laurent No\"{e}l\inst{2} \and Venceslas Biri\inst{2} \and Michel Couprie\inst{2}}
\institute{Universit\'{e} Paris 13, Sorbonne Paris Cit\'{e}, LAGA, CNRS(UMR 7539), \\ F-93430, Villetaneuse, France \\ \email{chaussard@math.univ-paris13.fr}
\and
Universit\'{e} Paris Est, LABINFO-IGM, A3SI-ESIEE \\ 2, boulevard Blaise Pascal, Cit\'{e} DESCARTES \\ BP 99  93162 Noisy le Grand CEDEX, France \\ \email{laurent.noel@esiee.fr, v.biri@esiee.fr, michel.couprie@esiee.fr}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                        %
%                   INTRODUCTION                         %
%                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec::intro}
Noise in photorealistic computer generated images. Need to accelerate convergence. Add knowledge of the geometry and topology of the scene thanks to discrete geometry. Use the skeleton. Need of a robust curvilinear skeleton that represent topology and approximate geometry. Use the cubical complex framework.
